---
title: "Download and Clean GSE70691"
author: "Jessica Scarborough"
date: "1/10/2022"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

Sys.setenv("VROOM_CONNECTION_SIZE" = 131072 * 10) # for downloading larger files

```


```{r packages, include=FALSE}
library(GEOquery)
library(limma)
library("maptools")  # point labels without overlaps
library(umap)
library(here)
library(tidyverse)


```

## Download Data

### GEO data 

```{r download_GSE, message=FALSE, warning=FALSE}
# load series and platform data from GEO
options(readr.show_col_types = FALSE)
GSE_num <- "GSE70691"

gset <- getGEO(GSE_num, GSEMatrix =TRUE, getGPL=TRUE, AnnotGPL = TRUE)
if (length(gset) > 1) idx <- grep("GPL14951", attr(gset, "names")) else idx <- 1
gset <- gset[[idx]]

phenotypes <- gset@phenoData@data
gene_table <- gset@featureData@data
gene_ids <- select(gene_table, ID, Symbol)


```


### Signature data 

Set variables to what is used in the manuscript signature, import that signature. 


```{r download_sig}


drug <- "Cisplatin"
de_comp_perc <- .20
rm_extreme_perc <- 0
sam_perm <- 10000
mult_perm <- 1000
n_folds <- 5

signature <- readRDS(file = here("Results", drug,
                                 paste0("intersect_sig_",
                                        "deCompPerc", (de_comp_perc*100),
                                        "_rmExtremePerc", rm_extreme_perc*100,
                                        "_samPerm", sam_perm,
                                        "_multPerm", mult_perm,
                                        "_nFolds", n_folds, ".rds")))

```

## Clean expression data 

### Log2 Transform if Necessary

Not required here


```{r log2_transform}

ex <- exprs(gset)
# log2 transform
qx <- as.numeric(quantile(ex, c(0., 0.25, 0.5, 0.75, 0.99, 1.0), na.rm=T))
LogC <- (qx[5] > 100) ||
  (qx[6]-qx[1] > 50 && qx[2] > 0)

if (LogC) { ex[which(ex <= 0)] <- NaN
ex <- log2(ex) }


```



### Plots

These plots ensure that the data are normalzed and the distribution is as expected. They are taken directly from the GEO2R code. 

```{r plot_expr}

# box-and-whisker plot
dev.new(width=3+ncol(gset)/6, height=5)
par(mar=c(7,4,2,1))
title <- paste (GSE_num, "/", annotation(gset), sep ="")
boxplot(ex, boxwex=0.7, notch=T, main=title, outline=FALSE, las=2)
dev.off()

# expression value distribution plot
par(mar=c(4,4,2,1))
title <- paste (GSE_num, "/", annotation(gset), " value distribution", sep ="")
plotDensities(ex, main=title, legend=F)

# mean-variance trend
ex <- na.omit(ex) # eliminate rows with NAs
plotSA(lmFit(ex), main=paste("Mean variance trend,", GSE_num))

# UMAP plot (multi-dimensional scaling)
ex <- ex[!duplicated(ex), ]  # remove duplicates
ump <- umap(t(ex), n_neighbors = 15, random_state = 123)

plot(ump$layout, main="UMAP plot, nbrs=15", xlab="", ylab="", pch=20, cex=1.5); pointLabel(ump$layout, labels = rownames(ump$layout), method="SANN", cex=0.6)

```

### Convert gene names

```{r convert_names}

ex_symbols <- data.frame(ex) %>%
  rownames_to_column("ID") %>%
  inner_join(gene_ids) %>%
  select(-ID)

```

### Extract signature expression

Below we check to see if all our signature genes are in this dataset. Here, it appears that all of our signature genes are in the database already, meaning we won't need to adjust the gene names. 

```{r check_genes}

signature %in% ex_symbols$Symbol

```

Let's extract expression of only our signature genes. 

```{r extract_sig_expr}

ex_sig <- ex_symbols %>%
  filter(Symbol %in% signature) %>%
  select(Symbol, everything())

```


### Clean signature expression

Now we can see that there are duplicate entries for some genes. For these genes, we'll take the mean of each entry. 


```{r median_expr_dups}

ex_sig_no_dups <- ex_sig %>%
  group_by(Symbol) %>%
  summarise(across(everything(), mean))

```

The last thing we'll do to clean this dataset is transpose the data so that genes are columns and samples are rows (the tidy format). 


```{r transpose_data}

ex_sig_tidy <- ex_sig_no_dups %>%
  pivot_longer(cols = -Symbol, names_to = "Sample_ID") %>%
  pivot_wider(names_from = Symbol, values_from = value)

```


## Phenotype data

### Clean phenotype data

```{r phenotype_clean}

phenotypes_tidy <- phenotypes %>%
  rename(tx = `treatment:ch1`,
         survival_mo = `survival (months):ch1`, 
         censor = `censor.os:ch1`,
         tissue = `tissue:ch1`) %>%
  select(title, Sample_ID = geo_accession, tx, survival_mo, censor, tissue)

```


## Combine data

Let's combine our phenotypes and gene expression into a single tidied dataset.

```{r combine_data}

data_tidy <- ex_sig_tidy %>%
  inner_join(phenotypes_tidy)

```


## Save Data


```{r save_data}

dir.create(here("Data", "GSE", GSE_num))

write.csv(ex_symbols, file = here("Data", "GSE", GSE_num, "gene_expr_all_raw.csv"),
          row.names = FALSE)

write.csv(ex_sig_tidy, file = here("Data", "GSE", GSE_num, "gene_expr_sig_tidy.csv"),
          row.names = FALSE)

write.csv(phenotypes, file = here("Data", "GSE", GSE_num, "phenotypes_raw.csv"),
          row.names = FALSE)

write.csv(phenotypes_tidy, file = here("Data", "GSE", GSE_num, "phenotypes_tidy.csv"),
          row.names = FALSE)

write.csv(data_tidy, file = here("Data", "GSE", GSE_num, "data_tidy.csv"),
          row.names = FALSE)

```